COVIDcast Indicators figures and tables

### 2021-09-27 indicators/code/indicator-paper-figures.Rmd
Remove code for old SafeGraph mobility map
Replaced with the vaccination acceptance/uptake graph.

## Now plot the each "as of" time series curve, faceted by state
dv_as_of %>%
  mutate(geo_label = factor(
    geo_value, levels = states,
    labels = abbr_to_name(states, ignore.case = TRUE))) %>%
  mutate(as_of = factor(format(as.Date(as_of), "%b %d"))) %>%
  ggplot(aes(x = time_value, y = value, color = as_of)) +
  geom_line() +
  facet_wrap(vars(geo_label), nrow = 2) +
  labs(color = "As of:", x = "Date", y = "% doctor's visits due to CLI") +
  expand_limits(y = 0) +
  scale_y_continuous(labels = label_percent(scale = 1, accuracy = 1),
                     breaks = seq(0, 12, by = 4)) +
  theme_bw() +
  theme(legend.pos = "bottom", legend.direction = "horizontal")

@@

Percentage point increase in SafeGraph estimates of the percentage of people
staying completely at home, based on aggregated mobile device data, between
March 1, 2020 and April 15, 2020.

```{r figure-6, message=FALSE, cache=TRUE}
begin_date <- "2020-03-01"
end_date <- "2020-04-15"

begin_data <- covidcast_signal("safegraph", "completely_home_prop_7dav",
                               begin_date, begin_date, geo_type = "state")
end_data <- covidcast_signal("safegraph", "completely_home_prop_7dav",
                             end_date, end_date, geo_type = "state")

diffs <- begin_data %>%
  inner_join(end_data, by = "geo_value", suffix = c(".begin", ".end")) %>%
  mutate(value = 100 * (value.end - value.begin)) %>%
  select(data_source = data_source.end, signal = signal.end, geo_value, value, issue = issue.end) %>%
  mutate(time_value = end_date) %>%
  as.data.frame %>%
  as.covidcast_signal(signal = "safegraph-change",
                      geo_type = "state")

plot(diffs, plot_type = "choro", range = c(10, 30),
     title = "", choro_params = list(legend_n = 5))

ggsave("../paper/fig/mobility-drop.pdf", width = 5, height = 4)
```

>>>>

## Now plot each "as of" time series curve, faceted by state
dv_as_of %>%
  mutate(geo_label = factor(
    geo_value, levels = states,
    labels = abbr_to_name(states, ignore.case = TRUE))) %>%
  mutate(as_of = factor(format(as.Date(as_of), "%b %d"))) %>%
  ggplot(aes(x = time_value, y = value, color = as_of)) +
  geom_line() +
  facet_wrap(vars(geo_label), nrow = 2) +
  labs(color = "As of:", x = "Date", y = "% doctor's visits due to CLI") +
  expand_limits(y = 0) +
  scale_y_continuous(labels = label_percent(scale = 1, accuracy = 1),
                     breaks = seq(0, 12, by = 4)) +
  theme_bw() +
  theme(legend.pos = "bottom", legend.direction = "horizontal")

@@
